Goals and Tasks

### 2020-05-12 README.Rmd
clipped task list
Re-Init Repo to match R Package Guidelines and include  roxygen syntax

## Tasks 
ignore this subheader

@@

## The Model

@@

>>>>

## Tasks

@@

@@

## Location Scale Regression Model

## Location Scale Regression Boost Model

```{r}
library(asp20boost)
model <- LocationScaleRegressionBoost$new(y ~ x, ~ x)
gradient_boost(model, 
              stepsize = 0.001, maxit = 1000,
              abstol = 0.001,
              verbose = FALSE)
plot(x, y)
lines(x,model$fitted_location)
#Todo do create similar graphic
curve(x + 1.96 * exp(x*model$gamma), -0.1, 1.1, add = TRUE)
curve(x - 1.96 * exp(x*model$gamma), -0.1, 1.1, add = TRUE)

```
